MLExplain

### 2018-05-24 paper.tex

\begin{figure*}
  \centering
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpreter and libraries (OCaml)};

@@

>>>>

% J'aime pas trop la voir tout en bas, mais ici ça fait bizarre, si tu as mieux
% je prends.

\begin{figure*}[ht]
  \centering
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpreter and libraries (OCaml)};

@@

The whole project takes the shape of a web application composed of the
JavaScript interpreter and a view. The view allows the user to write JavaScript
code and run it. It also displays the state of the program and the state of the
interpreter.

The program's execution is not interactive: when the button \texttt{run} is
pressed, the program is executed all at one and the traces are generated. Only
then, the user can replay the execution step by step.

This compiler offers several compilation modes:

\begin{itemize}
  \item \texttt{unlog}: generate JavaScript without tracing.
  \item \texttt{log}: generate JavaScript with tracing.
  \item \texttt{mlloc}, \texttt{token} and \texttt{ptoken}: generate files with
    informations about syntastical elements from the input file.
  \item \texttt{pseudo}: generate JavaScript enhanced with syntactic sugar for
    pattern matching or monadic operations -- it is supposed to be easier to
    read.
\end{itemize}

\subsubsection{fOCaml}
This compiler does not recognized the whole OCaml language, it can only handle
a small subset we named \texttt{fOCaml}. Among other restrictions, it cannot
handle objects and imperative features, exceptions, inner modules, and tuples.
